%------------------------------
%page 1
\begin{transparentFootline}
\begin{frame}
\frametitle{\noindent 论文发表情况(1/3)}

\footnotesize
\begin{enumerate}
\item \textbf{Weijing Huang}, Tengjiao Wang, Wei Chen, Siyuan Jiang, Kam-Fai Wong, PhraseCTM: Correlated Topic Modeling on Phrases within Markov Random Fields, ACL 2018, accepted. 
\item \textbf{Weijing Huang}, Tengjiao Wang, Wei Chen, Yazhou Wang, Category-Level Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection, DASFAA 2017. (EI index number: 20174404323179)
\item \textbf{Weijing Huang}, Wei Chen, Tengjiao Wang, Shibo Tao. TaxoPhrase: Exploring Knowledge Base via Joint Learning of Taxonomy and Topical Phrases, the 2nd Open Knowledge Base and Question Answering Workshop at SIGIR 2017.
\item \textbf{Weijing Huang}, Wei Chen, Tengjiao Wang, Shibo Tao. Efficient Topic Modeling on Phrases via Sparsity, the 29th IEEE International Conference on Tools with Artificial Intelligence (ICTAI) 2017. 
\item \textbf{Weijing Huang}, Wei Chen, Lamei Zhang, Tengjiao Wang, An Efficient Online Event Detection Method for Microblogs via User Modeling, the 18th Asia Pacific Web Conference (APWeb) 2016. (EI index number: 20164102880250)
\end{enumerate}
\end{frame}
\end{transparentFootline}

%------------------------------
%page 2
\begin{transparentFootline}
\begin{frame}
\frametitle{\noindent 论文发表情况(2/3)}

\footnotesize
\begin{enumerate}\addtocounter{enumi}{5}
\item Ruhui Wang, \textbf{Weijing Huang}, Wei Chen, Tengjiao Wang, Kai Lei. ASEM: Mining Aspects and Sentiment of Events from Microblog, the 24th ACM International Conference on Information and Knowledge Management (CIKM) 2015.
\item Yue Wang, \textbf{Weijing Huang}, Lang Zong, Tengjiao Wang, Dongqing Yang: Influence maximization with limit cost in social network. SCIENCE CHINA Information Sciences 56(7): 1-14 (2013) 
\item Yue Wang, \textbf{Weijing Huang}, Wei Chen, Tengjiao Wang,Dongqing Yang. Informed Prediction with Incremental Core-based Friend Cycle Discovering, the 12th International Conference on Web-Age Information Management (WAIM) 2011. 
\item 张腊梅，\textbf{黄威靖}，陈薇，王腾蛟，雷凯. EMTM：微博中与主题相关的专家挖掘方法. 计算机研究与发展. 2016年（第53卷）(萨师煊优秀学生论文奖).
\item 吴良, \textbf{黄威靖}, 陈薇, 王腾蛟, 雷凯, 刘月琴. ACT-LDA: 集成话题、社区和影响力分析的概率模型. 计算机科学与探索. 2013年第7卷第8期（718-728). 
\end{enumerate}
\end{frame}
\end{transparentFootline}

%------------------------------
%page 3
\begin{transparentFootline}
\begin{frame}
\frametitle{\noindent 论文发表情况(3/3)}

\footnotesize
\begin{enumerate}\addtocounter{enumi}{10}
\item Shibo Tao, Xiaorong Wang, \textbf{Weijing Huang}, Wei Chen, Tengjiao Wang, Kai Lei, From Citation Network to Study Map: A Novel Model to Reorganize Academic Literatures, Big Scholar workshop at WWW 2017.
\item Wei Chen, Lang Zong, \textbf{Weijing Huang}, Gaoyan Ou, Yue Wang, Dongqing Yang, An Empirical Study of Massively Parallel Bayesian Networks Learning for Sentiment Extraction from Unstructured Text, the 13th Asia-Pacific Web Conference (APWeb) 2011. 
\item Xilian Li, Wei Chen, Tengjiao Wang, \textbf{Weijing Huang}, Target-specific Convolutional Bi-directional LSTM Neural Network for Political Ideology Analysis, the Asia Pacific Web and Web-Age Information Management Joint Conference on Web and Big Data (APWeb-WAIM) 2017.
\item Xiao Zhang, Xiaorong Wang, Wei Chen, Jie Tao, \textbf{Weijing Huang}, Tengjiao Wang, A Taxi Gap Prediction Method via Double Ensemble Gradient Boosting Decision Tree, the 2nd IEEE International Conference on Intelligent Data and Security 2017.
\end{enumerate}
\end{frame}
\end{transparentFootline}

%------------------------------
%page 4
\begin{transparentFootline}
\begin{frame}
\frametitle{\noindent 参与科研项目情况}

硕博连读期间参与的项目：
\footnotesize
\begin{enumerate}
\item 非结构化数据管理系统北大部分——国家“核高基”重大专项(2010ZX01042-002-002-02)
\item 海量Web数据结构化内容提取与集成及大型示范应用——国家863计划课题(2012AA011002)
\item 微博用户社区及主题时序方法研究——中国信息安全测评中心合作项目
\item 大数据驱动的航天航空装备创新研发与应用示范——十三五国家重点研发计划课题
%\item 新一代互联网XX系统——国家科技支撑计划课题
%\item 微博XX系统——国家XX部合作项目
%\item 邮件XX系统——国家XX部合作项目
\end{enumerate}

\vfill

\normalsize
硕博连读期间参与的专利：
\footnotesize
\begin{enumerate}
\item 基于交互式文档聚类的信息检索方法及系统, \textbf{黄威靖}，于倩，陈薇，王腾蛟，杨冬青，CN103514183A.
\item Web社会网络核心用户信息交互演化分析方法，王悦，\textbf{黄威靖}，陈薇，王腾蛟，杨冬青，CN102637182A.
\end{enumerate}

\end{frame}
\end{transparentFootline}


